### 2017-12-03 monograph/thesis/chapters/beautifiers.tex
Created the section Language Server Protocol on beautifiers.tex
Fixed wrong \label creations over the project files.
Added some missing TODO statements and creates lists for loose URLs
Added new link references to the Language Server Protocol section

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\label{source_code_beautifiers}
\chapter{Source Code Beautifiers}

@@

@@

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Source Code Beautifiers}
\label{source_code_beautifiers}

@@

    TODO.

@@

    \section{Language Server Protocol}

    TODO.

    \url{https://www.youtube.com/watch?v=2GqpdfIAhz8}
    \url{http://langserver.org/}
    \url{https://github.com/Microsoft/language-server-protocol}
    \url{https://github.com/SublimeCodeIntel/SublimeCodeIntel}
    \url{https://code.visualstudio.com/blogs/2016/06/27/common-language-protocol}
    \url{https://www.eclipse.org/community/eclipse_newsletter/2017/may/article1.php}
    \url{https://github.com/Microsoft/language-server-protocol/wiki/Protocol-Implementations}
